### 2013-05-21 Problems.tex
Some more questions

\item From this description can we read off various properties of the torus: ramified vs unramified, anisotropic, character and cocharacter lattice....

@@

>>>>

\item From this description can we read off various properties of the torus: ramified vs unramified, anisotropic, character and cocharacter lattices, N\'eron model....

@@

\item For anisotropic tori can you describe the reduction of the maximal compact containing this torus?
